DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-05-11 paper/ootavacuous.tex
ootavacuous: Sections 2.2.1/2.2.2: Use z=x*y to be consistent with y=f(x)
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Some discussions of semantic dependencies assume that they
are strictly functions of the source code.
This assumption is not always valid, in fact, we will see that many
instances of semantic dependency must be considered functions of
particular executions.
Consider for example:
\begin{quote}
\begin{verbatim}
x = y * z;
\end{verbatim}
\end{quote}

Expanding on earlier discussions~\cite{Boehm:2014:OGA:2618128.2618134},
as long as \co{z} is zero, changes in the
value of \co{y} will not cause a change in the value stored to \co{x}.
As a result, the semantic dependency from \co{y} to \co{x} exists only
in executions where \co{z} is nonzero,
which shows it is a property of the execution, not just of the source code.

@@

Suppose that in some execution of the previous example,
both \co{y} and \co{z} are zero.
Then changes to either \co{y} or \co{z}
will not cause a change in the value stored to \co{x}.
In other words, in this execution there is no semantic dependency
from either \co{y} or \co{z} to \co{x}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{y},~\co{z}\} to \co{x},
because changes to both \co{y} and \co{z}
can cause the value stored in \co{x} to change.
This means that, prior work~\cite{PaulEMcKenney2016OOTA}
notwithstanding, accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must at times consider changes to multiple variables.
% @@@  Pull anything in?  Doesn't seem necessary.
% See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
% for examples and additional discussion.

>>>>

Some discussions of semantic dependencies assume that they
are strictly functions of the source code.
This assumption is not always valid, in fact, we will see that many
instances of semantic dependency must be considered functions of
particular executions.
Consider for example:
\begin{quote}
\begin{verbatim}
z = x * y;
\end{verbatim}
\end{quote}

Expanding on earlier discussions~\cite{Boehm:2014:OGA:2618128.2618134},
as long as \co{y} is zero, changes in the
value of \co{x} will not cause a change in the value stored to \co{z}.
As a result, the semantic dependency from \co{x} to \co{z} exists only
in executions where \co{y} is nonzero,
which shows it is a property of the execution, not just of the source code.

@@

Suppose that in some execution of the previous example,
both \co{x} and \co{y} are zero.
Then changes to either \co{x} or \co{y}
will not cause a change in the value stored to \co{z}.
In other words, in this execution there is no semantic dependency
from either \co{x} or \co{y} to \co{z}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{x},~\co{y}\} to \co{z},
because changes to both \co{x} and \co{y}
can cause the value stored in \co{z} to change.
This means that, prior work~\cite{PaulEMcKenney2016OOTA}
notwithstanding, accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must at times consider changes to multiple variables.
% @@@  Pull anything in?  Doesn't seem necessary.
% See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
% for examples and additional discussion.
